A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-05-17 methodology.tex
reviewer2 - major revisions -- revision#3 -- better explanation

Figure~\ref{fig:extraction} illustrates path extraction on a simple change. The change replaces \verb+tail+ with \verb+&tail+ and \verb+head+ with \verb+head.clone()+. That is, after the change, the second argument passes a borrow of \verb+tail+ rather than sending the ownership of \verb+tail+ to the callee; and, the third argument sends a clone of head to the callee instead of sending head itself. A DFS on this tree yields three different paths, which we show in red, green, and purple. A path represents a sequence of involved non terminals. It is crucial to record the order of nodes in the path, so that we could record that order in our datapoint embedding.

@@

We propose a novel representation. Similar to the naive approach, we order-insensitively define the columns of our dataset as the set of items $\mathtt{NT} \cup \mathtt{BCE}$ we collected from Syn (the columns are constant across all Rust programs). However, to simulate order-sensitiveness, we add two more steps. First, we record the number of occurrences of items within the paths at each scope. The reason behind this decision is because a different order of program elements yields a different number of occurrences of underlying dimension. Second, we semi-automatically design a weighting scheme to prioritize non terminals that we think are more salient for Rust bugs. Section~\ref{sec:weighting_scheme}, immediately below, illustrates this approach on an example.

>>>>

Figure~\ref{fig:extraction} illustrates path extraction on a simple change. The change replaces \verb+tail+ with \verb+&tail+ and \verb+head+ with \verb+head.clone()+. That is, after the change, the second argument passes a borrow of \verb+tail+ rather than sending the ownership of \verb+tail+ to the callee; and, the third argument sends a clone of head to the callee instead of sending head itself. A DFS on this tree yields three different paths, which we show in red, green, and purple. A path represents a sequence of involved non terminals. It is crucial to record the order of nodes in the path, so that we could record that order in our datapoint embedding. Note that the tree depicted in Figure~\ref{fig:extraction} is not an AST; rather, it represents an ASTDiff. The number of paths in the ASTDiff does not directly correspond to the number of changed elements in the source code. Instead, it is determined by the structural differences between the two ASTs of the code versions. The paths in the ASTDiff capture the changes in the code structure between the two versions, allowing us to analyze and extract relevant information for further processing.

@@

We propose a novel representation. Similar to the naive approach, we define the columns of our dataset as the set of items $\mathtt{NT} \cup \mathtt{BCE}$ collected from Syn. However, to account for order-sensitivity, we introduce two additional steps. Firstly, we record the number of occurrences of items from $\mathtt{NT} \cup \mathtt{BCE}$ within each root-level scope. This captures the varying occurrence counts resulting from different element orders in the program. Secondly, we incorporate a weighting scheme, designed semi-automatically, to prioritize non-terminals that we consider more salient for Rust bugs. Section~\ref{sec:weighting_scheme}, immediately below,
illustrates this approach on an example.

### 2023-05-17 results.tex
reviewer2 - minor revision#4 - compares --> inspects
reviewer2 - major revisions -- revision#3 -- better explanation

Our evaluation aims to determine whether the most important program elements get high values in our embedding, i.e. are recognized as important. A human analyzer (paper author) compares the actual change in the code and compares it to the visual representation of the respective data point. We used circle pack figures to visualize each data point~\citep{collins2003circle}, generated with the packcircles python library\footnote{\url{https://github.com/mhtchan/packcircles}}. In these figures, the radius of the circle for each non terminal shows its importance in our embedding (Figure~\ref{fig:essence} presented an example of the circle pack figures).

@@

\noindent\textbf{Description:} This is a change that in all instances (in our benchmarks) has been proposed by Clippy---commit messages indicated the use of Clippy for this fix. The change applies on an object prior to calling \verb+to_string()+ on that object. In this change, a dereference operator is added to that object. The reason behind the change is that the object is a reference type of \verb+T+, while \verb+T+ directly implements \verb+to_string()+. Adding the dereference makes the compiler use the specialized implementation of \verb+to_string()+ and not go through slower string formatting methods.

>>>>

Our evaluation aims to determine whether the most important program elements get high values in our embedding, i.e. are recognized as important. A human analyzer (paper author) inspects the actual change in the code and compares it to the visual representation of the respective data point. We used circle pack figures to visualize each data point~\citep{collins2003circle}, generated with the packcircles python library\footnote{\url{https://github.com/mhtchan/packcircles}}. In these figures, the radius of the circle for each non terminal shows its importance in our embedding (Figure~\ref{fig:essence} presented an example of the circle pack figures).

@@

\noindent\textbf{Description:} This is a change that in all instances (in our benchmarks) has been proposed by Clippy---commit messages indicated the use of Clippy for this fix. The change applies on an object prior to calling \verb+to_string()+ on that object. In this change, a dereference operator is added to that object. The reason behind the change is that the object is a reference type of \verb+T+, while \verb+T+ directly implements \verb+to_string()+. Adding the dereference makes the compiler use the specialized implementation of \verb+to_string()+ and not go through slower string formatting methods\footnote{\url{https://rust-lang.github.io/rust-clippy/master/index.html\#inefficient\_to\_string}}.
